\documentclass[letterpaper]{article}
\title{Darkness under Windygale}
\author{Bill Tyros}
\date{\vspace{-5ex}}

\usepackage{varioref}
\usepackage{xcolor}
\usepackage[margin=.5in]{geometry}
\usepackage{multicol}
\usepackage{pifont}
\usepackage{mdframed}
\mdfdefinestyle{BoxedText}{%
    linecolor=black,
    outerlinewidth=10pt,
    roundcorner=10pt,
    innertopmargin=5pt,
    innerbottommargin=5pt,
    innerrightmargin=7.5pt,
    innerleftmargin=7.5pt,
    backgroundcolor=white}

\renewcommand{\labelitemi}{\ding{42}}

\begin{document}
	\begin{multicols}{2}
	\maketitle
	\section{Valley of Prosperity}
		\begin{mdframed}[style=BoxedText]
		        A sheer cliff dips hundred of feet below you leading to a dry valley, an \textbf{imposing castle} and a \textbf{massive clock tower} loom over a \textbf{bustling town} surrounded by cacti farms as far as the eye can see, a \textbf{leaning tower} rises above the flat land surrounded by a few stone buildings and a sea of misshappen megaliths, a glowing darkness rises above a \textbf{deep dark hole} in the ground with fissures spiraling outwards all around it.
		\end{mdframed}
		\begin{itemize}
		  \item \textbf{Imposing Castle.~\vref{location-castle}} Castle Greypoint.
		  \item \textbf{Massive Clock Tower.~\vref{location-temple}} Temple of Jorike.
		  \item \textbf{Bustling Town.~\vref{location-town}} Windygale.
		  \item \textbf{Deep Dark Hole.~\vref{location-caves}} Quaking Caves.
		\end{itemize}
		\section{Castle Greypoint~\label{location-castle}}
				\begin{mdframed}[style=BoxedText]
					A high castle overlooks the surrounding town, a large tower between four turrets rises above a \textbf{gatehouse} leading to an \textbf{inner courtyard} with a stable and paths leading to the \textbf{guard's quarters} and the \textbf{lord's apartments}.
				\end{mdframed}
					 \begin{itemize}
						  \item \textbf{Gatehouse.} 1 \textbf{knight} and 4 guards standing watch, won't let anyone inside the castle without a reason (bounty, letter of recommendation, etc.).
						  \begin{itemize}
						  	\item \textbf{Knight.} \textit{High Knight Percival}. Bored, resents being assigned this post which is beneath his status.
						  \end{itemize}
						  \item \textbf{Inner Couryard.} Temple of Jorike.
						  \item \textbf{Guard's Quarters.} Windygale.
						  \item \textbf{Lord's Apartments.} Quaking Caves.
				 \end{itemize}

			\section{Temple of Jorike~\label{location-temple}}
				\begin{mdframed}[style=BoxedText]
					Blah
				\end{mdframed}
			\section{Windygale~\label{location-town}}
				\begin{mdframed}[style=BoxedText]
					Blah
				\end{mdframed}
			\section{Quacking Caves~\label{location-caves}}
				\begin{mdframed}[style=BoxedText]
				\end{mdframed}
	\end{multicols}
\end{document}